The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-06-03 paper/ms.tex
paper: add lc provenance paragraphs

>>>>

\paragraph{Light curve provenance}.
In Sector 6, about 49{,}000 light curves of candidate cluster stars
were made. The provenance of the claimed cluster origin of these
sources is \citet{dias_proper_2014} for 59\% of the sources;
\citet{zari_3d_2018} for 16\% of sources from their upper
main-sequence table and 1\% of sources from their PMS table;
\citet{Kharchenko_et_al_2013} for 8\% of sources,
\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
catalogs for the remaining 10\% of sources.

The clusters with the largest claimed numbers of sources are the
Platais~6, Platais~5, and Mamajek~3 moving groups, all from
\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
respectively. These membership claims should be regarded with some
skepticism on a source-by-source basis.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (32$\,$Ori) has only about 50 confirmed members
\citep{bell_32ori_2017}.

We remind the reader that our goal in creating this sample was
completeness, rather than fidelity. The \citet{dias_proper_2014} stars
in particular were included if they were listed with membership
probability exceeding 50\%.  To create cleaner sub-samples, we advise
use of the \texttt{CDEXTCAT} header keyword, which can be
cross-matched against the original source catalog to obtain the
membership probabilities claimed by the original catalog.
